`sdmTMB`: Fast, flexible, and user-friendly spatial and spatiotemporal generalized linear mixed-effects models

### 2021-08-04 doc/paper.Rmd
Add some VAST notes

-   how it achieves the steps Jim described [@thorson2019] in what a VAST-related package has to be able to do (and how VAST does it vs. how sdmTMB does it)

>>>>

-   how it achieves the steps Jim described [@thorson2019] in what a VAST-related package has to be able to do (and how VAST does it vs. how sdmTMB does it)
    -   "VAST represents four main design principles. Although there are many other implementation details that distinguish VAST from previous index-standardization methods, I believe that these four design principles represent the features that any future replacement should include."
    -   Area weighting (check, helper functions to sum up weighted grid cells)
    -   Distinct catchability and habitat covariates (check, decide what goes into `predict()`)
    -   Condition on missing covariates (check, random fields)
    -   Bridge between univariate and multivariate applications (no! should we?)
